Figure 6 - heterodimer

### 2024-07-04 ms_figure_7_heterodimer.Rmd
rename figs2-6 to figs3-7
Co-authored-by: Charlotte Soneson <charlottesoneson@gmail.com>
Co-authored-by: Michael Stadler <stadler.michael@gmail.com>

(p_zone <- ggplot(zone_avg, aes(fill = Zone, y = 100 * avg_fraction_by_zone, 
                                x = Condition)) + 
     geom_bar(position = "stack", stat = "identity") +
     labs(title = "Relative zone distribution\nincl. both replicates", 
          x = "", y = "Relative distribution [%]") +
     scale_fill_manual(values = c(main_colors[1], main_colors[3], main_colors[5]),
                       name = "") + 
     scale_x_discrete(labels = get_xlabs) + 
     theme_cowplot() + 
     theme(axis.text.x = element_markdown()))
```

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        gg_ipdimer, 
        fig6c,
        nrow = 1, 
        rel_widths = c(1, 2), 
        labels = c("A", "C"),
        align = "h", axis = "bt"
    ),
    cowplot::plot_grid(
        fig6b, 
        gcov,
        rel_widths = c(1, 1),
        labels = c("B", "D")
    ),
    cowplot::plot_grid(
        fig6e,
        NULL,
        fig6f,
        NULL,
        p_rel_dis,
        labels = c("E", "", "F", "", "G"),
        # rel_widths = c(7.65, 0.5, 1.45, 0.5, 9)
        rel_widths = c(6, 0.75, 1.2, 0.75, 10.4), nrow = 1
    ), 
    ncol = 1
)
```

@@

```{r suppFig6}
#| fig.width: 13
#| fig.height: 10
#| warning: false

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        figs6a, 
        NULL,
        p_zone + theme(legend.position = "top"), 
        nrow = 1, 
        rel_widths = c(1.75, 0.25, 1.25), 
        labels = c("A", "", "B")
    ),
    cowplot::plot_grid(
        genomeplot_tpm,
        gcovdel,
        # maplots$ID83delTMD,
        nrow = 1, 
        rel_widths = c(1.2, 1),
        labels = c("C", "D")
    ),
    ncol = 1, rel_heights = c(1, 0.7)
)
```

>>>>

get_xlabs_bar <- function(x) {
    vapply(x, function(xx) sub("\n", "<br>", paste0("*", xx, "*", "<br>(n = ", 
                                                    length(which(dist_ne$Condition == xx)), ")"), fixed = TRUE), "")
}

(p_zone <- ggplot(zone_avg, aes(fill = Zone, y = 100 * avg_fraction_by_zone, 
                                x = Condition)) + 
     geom_bar(position = "stack", stat = "identity") +
     geom_text(aes(label = paste0(round(100 * avg_fraction_by_zone, 2), "%")), 
                   position = position_stack(vjust = 0.5), size = 4) +
     labs(title = "Relative zone distribution incl. both replicates", 
          x = "", y = "Relative distribution [%]") +
     scale_fill_manual(values = c(main_colors[1], main_colors[3], main_colors[5]),
                       name = "") + 
     scale_x_discrete(labels = get_xlabs_bar) + 
     theme_cowplot() + 
     theme(axis.text.x = element_markdown()))
```

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        gg_ipdimer, 
        fig6c,
        nrow = 1, 
        rel_widths = c(1, 2), 
        labels = c("A", "C"),
        align = "h", axis = "bt"
    ),
    cowplot::plot_grid(
        fig6b, 
        gcov,
        rel_widths = c(1, 1),
        labels = c("B", "D")
    ),
    cowplot::plot_grid(
        fig6e,
        NULL,
        fig6f,
        NULL,
        p_zone + theme(legend.position = "top"), 
        labels = c("E", "", "F", "", "G"),
        # rel_widths = c(7.65, 0.5, 1.45, 0.5, 9)
        rel_widths = c(6, 0.75, 1.2, 0.75, 10.4), nrow = 1
    ), 
    ncol = 1
)
```

@@

```{r suppFig6}
#| fig.width: 13
#| fig.height: 9
#| warning: false

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        figs6a, 
        NULL,
        p_rel_dis,
        nrow = 1, 
        rel_widths = c(1.55, 0.25, 1.45), 
        labels = c("A", "", "B")
    ),
    cowplot::plot_grid(
        genomeplot_tpm,
        gcovdel,
        # maplots$ID83delTMD,
        nrow = 1, 
        rel_widths = c(1.2, 1),
        labels = c("C", "D")
    ),
    ncol = 1, rel_heights = c(1, 1)
)
```
